---
title: "Class Four Markdown exploration"
author: "Richard Todd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: sage_dioa18_44.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(tidyverse)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
  tidy = FALSE, cache.extra = packageVersion('tufte'),
  echo = FALSE,
  collapse=TRUE, 
  warning=FALSE)
options(htmltools.dir.version = FALSE)
```

# Summary

It's nice to explore the different layout options. Captions are placed inthe margin.

```{r starwars-plot, fig.margin = FALSE, fig.cap = "Fig. 1: Star Wars character mass vs height", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE}
ggplot(starwars,aes(x=height,y=mass)) + geom_point()

```

The layout of this template is a little mysterious. With more time and effort, we might decipher it fully. Instead, we will discharge only our class responsibilities. The chart above helps us to do this.


# Tables

This is a wonderful example of Tufte table.

```{r starwarstable, cache = TRUE, fig.cap = "Tab. 1: Star Wars mass and unique species by planet"}

knitr::kable(head(starwars %>%
  group_by(homeworld) %>%
  summarise(total_mass = sum(mass),no_species = n_distinct(species)),10),
  caption = "Mass by Starwars species")

```

That was fun.

Now look at the table above, referred to in the margins. For more examples see @Makarius1970 or @Bintliff1993.


```{r reading-chunks}
knitr::read_chunk("w4_chunk_to_read.r")
```
